---
title: "BeerData"
author: "Atsu Atakpa"
date: "June 27, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis information for Breweries and Beers
```{r, echo=FALSE}
library(readxl)
Beers <- read_excel("~//SMU//Doing DataScience//Case Study 1//CaseStudy1//Data//Beers.xlsx")
Breweries <- read_excel("~//SMU/Doing DataScience//Case Study 1//CaseStudy1//Data//Breweries.xlsx")
BB_Data <- merge(Breweries, Beers, by = c("Brewery_id"), all =TRUE)

```

## Number of Breweries in each state
```{r, echo=FALSE}
library(plyr)
count(Breweries, "State")
```
## First 6 Observations of Merged Data
```{r, echo=FALSE}
head(BB_Data,6)
```
## Last 6 Observations of Merged Data
```{r, echo=FALSE}
tail(BB_Data,6)
```
## Count of NA's in each column
```{r, echo=FALSE}
sapply(BB_Data,function(x) sum(is.na(x)))
```
## Median ABV and IBU by state
```{r, echo=FALSE}
aggregate(BB_Data[, 7:8],list(BB_Data$State), median, na.rm = TRUE)

```
## Plot (needs work)
```{r, echo=FALSE}
median_ABU_IBU <-aggregate(BB_Data[, 7:8],list(BB_Data$State), mean, na.rm = TRUE)

barplot(median_ABU_IBU$IBU)

barplot(median_ABU_IBU$ABV)
```

## State with the maximum alcoholic beverage
```{r, echo=FALSE}
attach(BB_Data)
BB_Data[which(BB_Data$ABV == max(BB_Data$ABV, na.rm = TRUE)) ,"State"]

```
## State with the most bitter beer
```{r, echo=FALSE}
attach(BB_Data)
BB_Data[which(BB_Data$IBU == max(BB_Data$IBU, na.rm = TRUE)) ,"State"]
```
## Summary statistics of ABV
```{r, echo=FALSE}
summary(BB_Data$ABV)
```


## Plot of ABV and IBU

You can also embed plots, for example:

```{r, echo=FALSE}
plot(BB_Data$ABV, BB_Data$IBU, main = 'Plot of ABV and IBU',xlab = 'Alcohol By Volume(ABV)', ylab = 'International Bittering Units(IBU)', col = "dark blue",lwd = 1)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
