---
title: "BeerData"
author: "Atsu Atakpa"
date: "June 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis information for Breweries and Beers

The information provided in this document is an analysis of Beers and Breweries dataset to gain insight into the data. To provide information contained in the data we will apply some statistical methods of analyzing data and provide some visual evidence to support the analysis. The data is imported into R for both the Beers and Breweries and we used a merge to combine both datasets.

```{r}
# Code to import the Beers and Breweries dataset
library(readxl)
Beers <- read_excel("~//SMU//Doing DataScience//Case Study 1//CaseStudy1//Data//Beers.xlsx")
Breweries <- read_excel("~//SMU/Doing DataScience//Case Study 1//CaseStudy1//Data//Breweries.xlsx")
# merges the Beers and Breweries Data
BB_Data <- merge(Breweries, Beers, by = c("Brewery_id"), all =TRUE)

```

## Number of Breweries in each state
We first want to find the number of Breweries by state. We will run a count on the dataset Breweries. This will give us an idea as to the how the results provided will differ or be similar state by state.
```{r}
library(plyr)
count(Breweries, "State")
```

## First 6 Observations of Merged Data
To test that the merge of our Beers and Breweries dataset was properly done, we will check the results of the first six data in the dataset BB_Data

```{r}
head(BB_Data,6)
```
## Last 6 Observations of Merged Data
We will also print out the last six results from the merge to confirm that our data merged well.

```{r}
tail(BB_Data,6)
```
## Count of NA's in each column
The result below will tell us how many missing records for each column that we will be working with.

```{r}
sapply(BB_Data,function(x) sum(is.na(x)))
```

## Median ABV and IBU by state
For each state the table below shows the calculation of the median results for ABV and IBU
```{r}
aggregate(BB_Data[, 7:8],list(BB_Data$State), median, na.rm = TRUE)

```
## Plot (needs work)
```{r, echo=FALSE}
median_ABU_IBU <-aggregate(BB_Data[, 7:8],list(BB_Data$State), mean, na.rm = TRUE)

barplot(median_ABU_IBU$IBU)

barplot(median_ABU_IBU$ABV)
```

## State with the maximum alcoholic beverage
To find the state with the maximum alcoholic beverage we will run the code below to give us the maximum value in the ABV Colum of the BB_Dataset and return the result by state
```{r}
attach(BB_Data)
BB_Data[which(BB_Data$ABV == max(BB_Data$ABV, na.rm = TRUE)) ,"State"]

```
## State with the most bitter beer
To find the state with the most bitter beer, we will run the code below to give us the maximum value in the IBU column of the BB_Dataset and return the result by state
```{r}
attach(BB_Data)
BB_Data[which(BB_Data$IBU == max(BB_Data$IBU, na.rm = TRUE)) ,"State"]
```

## Summary statistics of ABV
The summary statistic of the alcohol by volume is provided below with a 5 number summary and number of missing values.
```{r}
summary(BB_Data$ABV)
```


## Plot of ABV and IBU

Determination of relationship between two dataset is enhanced using some visual evidence. We will use a scatter plot to give us a visual perspective.

```{r}
plot(BB_Data$ABV, BB_Data$IBU, main = 'Plot of ABV and IBU',xlab = 'Alcohol By Volume(ABV)', ylab = 'International Bittering Units(IBU)', col = "dark blue",lwd = 1)

library(ggplot2)
g <- ggplot(BB_Data, aes(x = BB_Data$ABV, y = BB_Data$IBU), na.rm=TRUE) + geom_point() + geom_smooth(method="lm")  # set se=FALSE to turnoff confidence bands
plot(g)

```
